method

### 2021-12-06 06_Paper/ER-ED/method.Rmd
added figure

effort_Reg = data_ER %>%
  subset(data_ER$block != "view_neu" & data_ER$block != "choice")

aov.effort = afex::aov_ez(id = "ID",
                          dv = "effort",
                          data = effort_Reg,
                          within = "block",
                          fun_aggregate = mean)
afex::nice(aov.effort, es = "pes")

# compute posthoc tests for within measure
posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
pairs(posthoc_effort, adjust = "bonferroni")
```

>>>>

effort_reg = data_ER %>%
  subset(data_ER$block != "view_neu" & data_ER$block != "choice")

aov.effort = afex::aov_ez(id = "ID",
                          dv = "effort",
                          data = effort_reg,
                          within = "block",
                          fun_aggregate = mean)
afex::nice(aov.effort, es = "pes")

# compute posthoc tests for within measure
posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
pairs(posthoc_effort, adjust = "bonferroni")

# Figure to visualize effort ratings
# figure
ggplot2::ggplot(effort_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")
```
